\LaTeX\ Author Guidelines for ICCV Proceedings

### 2021-02-19 chapters/supplementary.tex
Add first version of new alg. and binary tree formulation
Several changes to alg. descr and linkages

\begin{algorithm*}
  \caption{Implementation of \algname{}, generalized algorithm for signed graph partitioning}
\hspace*{\algorithmicindent} \textbf{Input:} $\mathcal{G}(V,E,w^+,w^-)$ with $N$ nodes and $M$ edges; boolean \texttt{{\color{blue}addCannotLinkConstraints}} \\
\hspace*{\algorithmicindent} \textbf{Output:} Final clustering \\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]
      \State $\tilde{\mathcal{G}}(\tilde{V},\tilde{E}) \gets \mathcal{G}(V,E,w^+,w^-)$  \Comment{Init. contracted graph}
      \State \texttt{UF} $\gets$ initUnionFind($V$) \Comment{Init. data structure representing clustering}
        \State PQ.push$(|w_e|, e) \quad \forall e \in E $  \Comment{Init. priority queue in desc. order of $|w_e|=|w_e^+ - w_e^-|$, $\mathcal{O}(|E|)$}
        \State \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$ \Comment{Init. cannot-link constraints}
    \State
      \While{PQ is \textbf{not} empty}
        \State $\tilde{w}, e_{uv} \gets $ PQ.popHighest() \Comment{$\mathcal{O}(\log |E|)$}
        \State \textbf{assert} \texttt{UF}.find($u$) $\neq$ \texttt{UF}.find($v$) \Comment{Edges in PQ always link nodes in different clusters}
        \If{({\color{ForestGreen}\textbf{$\tilde{w} > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
          \State PQ, \texttt{canBeMerged}, $\tilde{E}$ $\gets$ \textsc{UpdateNeighbors}($u,v$)
          \State $\tilde{V} \gets \tilde{V} \setminus \{ v\}$, $\quad \tilde{E} \gets \tilde{E} \setminus \{ e_{uv}\}$ \Comment{Update contracted graph}
          \State \texttt{UF}.merge($u,v$) \Comment{Merge clusters, $\mathcal{O}(\alpha(|E|))$}
        \ElsIf{({\color{red}\textbf{$\tilde{\cost} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLinkConstraints}}}
          \State \texttt{canBeMerged}$[e_{uv}] \gets$ \texttt{False} \Comment{Constrain the two clusters}
        \EndIf
      \EndWhile
      \State
      \Return Final clustering given by union-find data structure  \texttt{UF}
  \end{algorithmic}
  \hspace*{1.5cm} 
    \begin{algorithmic}[1]
    \Function{UpdateNeighbors}{$u,v$}
      \State $\mathcal{N}_u = \{ t \in \tilde{V} | e_{ut}\in \tilde{E}  \}$
      \State $\mathcal{N}_v = \{ t \in \tilde{V} | e_{vt}\in \tilde{E}  \}$ 
      \For{$t \in \mathcal{N}_v$ } \Comment{Loop over neighbors in $\tilde{\mathcal{G}}$ of deleted node $v$}
        \State $\tilde{E} \gets \tilde{E} \setminus \{e_{vt}\}$
        \State $\tilde{w}_{vt} \gets$ PQ.delete($e_{vt}$) \Comment{$\mathcal{O}(\log |E|)$}
        \State \texttt{canBeMerged}$[e_{ut}] \gets$ \texttt{canBeMerged}$[e_{ut}]$ \textbf{and} \texttt{canBeMerged}$[e_{vt}]$
        \If{$t \in \mathcal{N}_u$ }\Comment{$t$ is a common neighbor of $u$ and $v$}
          \State $\tilde{w}_{ut} \gets$ PQ.delete($e_{ut}$)  \Comment{$\mathcal{O}(\log |E|)$}
          \State PQ.push($ |f(\tilde{w}_{ut}, \tilde{w}_{vt})|, e_{ut}$) \Comment{$\mathcal{O}(\log |E|)$  }
        \Else
          \State $\tilde{E} \gets \tilde{E} \cup \{e_{ut}\}$
          \State PQ.push($ |\tilde{w}_{vt}|, e_{ut}$) \Comment{$\mathcal{O}(\log |E|)$}
        \EndIf
      \EndFor
      \State
      \Return PQ, \texttt{canBeMerged}, $\tilde{E}$
    \EndFunction
  \end{algorithmic}
  \label{detailed_alg}
\end{algorithm*}

@@

\begin{figure*}[t]
        \centering
        \includegraphics[width=0.7\textwidth]{./figs/proof_abs_max_example.pdf} % left bottom right top
\caption{\algname{} with \emph{AbsMax} linkage: Example representing the only case of edge contraction $e_{uv}$ that would introduce a positive attractive interaction between two constrained clusters. Note this can actually never happen with an \emph{AbsMax} linkage, because edge $e_{ut}$ has a lower absolute priority as compared to $e_{uv}$, so clusters $u$ and $t$ cannot have been constrained before $u$ and $v$ are merged.
}
\label{fig:abs_max_proof_example}  
\end{figure*}
\begin{algorithm*}[t]
  \caption{Mutex Watershed Algorithm proposed by \cite{wolf2018mutex}}
\hspace*{\algorithmicindent} \textbf{Input:} $\mathcal{G}(V,E,w^+,w^-)$ with $N$ nodes and $M$ edges \\
\hspace*{\algorithmicindent} \textbf{Output:} Final clustering \\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]
      \State \texttt{UF} $\gets$ initUnionFind($V$) 
      \For{$(u,v)=e\in E$ in descending order of $|w_e|=|w_e^+ - w_e^-|$}
        \If{\texttt{UF}.find($u$) $\neq$ \texttt{UF}.find($v$)} \Comment{Check if $u,v$ are already in the same cluster}
          \If{({\color{ForestGreen}\textbf{$w_e > 0$}}) \textbf{and} \texttt{canBeMerged}($u,v$)}  \Comment{Check for cannot-link constraints}
            \State \texttt{UF}.merge($u,v$) and inherit constraints of parent clusters
          \ElsIf{({\color{red}\textbf{$w_e \leq 0$}})}
            \State Add cannot-link constraints between parent clusters of $u,v$
          \EndIf
        \EndIf
      \EndFor
      \State
      \Return Final clustering given by union-find data structure \texttt{UF}
  \end{algorithmic}
  \label{alg:mutex_watershed}
\end{algorithm*}

@@

In the field of image processing there are several ways of adding noise to an image, among which the most common are Gaussian noise or Poisson shot noise. 
In these cases, the noise of one pixel does not correlate with its neighboring noise values. On the other hand, predictions of a CNN are known to be spatially correlated. 
Thus, we used Perlin noise\footnote{In our experiments, we used an open-source implementation of simplex noise \cite{perlin2001noise}, which is an improved version of Perlin noise \cite{perlin1985image}}, one of the most common gradient noises used in procedural pattern generation. This type of noise $n(x)\in[0,1]$ generates spatial random patterns that are locally smooth but have large and diverse variations on bigger scales. We then combined it with the CNN predictions $p(x)$ in the two following ways: 
\begin{equation}\label{eq:noise_biased_predictions}
\tilde{F}_{\pm}(x;\mathcal{K})=F(x)\pm\big|\mathcal{K}\cdot\max\left(\pm N(x),0\right)\big|,
\end{equation}
where  $N(x)=\mathrm{Logit}[n(x)]$; $F(x)=\mathrm{Logit}[p(x)]$ and $\mathcal{K}\in \mathbb{R}^+$ is a positive factor representing the amount of added noise. $\tilde{F}_{+}(x;\mathcal{K})$ represents then a under-clustering biased prediction, such that the probability for two pixels to be in the same cluster is increased only if $N(x)>0$ (see Fig. \hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}b}), whereas $\tilde{F}_{-}(x;\mathcal{K})$ is a over-clustering biased prediction with decreased probabilities when $N(x)<0$ (Fig. \hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}c}).
In the implementation we used, the noise can be generated in an arbitrary number of dimensions and a smoothing factor can be specified for each direction independently. In our experiments, each pixel is represented by a node in the grid-graph and it is linked to $n_{\mathrm{nb}}$ other nodes by short- and long-range edges. Thus, the output of our CNN model has $n_{\mathrm{nb}}$ channels: for each pixel / voxel, it outputs $n_{\mathrm{nb}}$ values representing the weights of different edge connections. We then generated a 4-dimensional noise that matches the dimension of the CNN output. The data is highly anisotropic, i.e. it has a lower resolution in one of the dimensions. Due to this fact, we chose different smoothing parameters to generate the noise in different directions.

The experiments summarized in Fig. \ref{fig:noise_plots} were performed in the following way: for each value $\mathcal{K}$, 30 random noise samples were drawn, from which median and percentiles statistics were computed for each different linkage criteria. For each sample, we randomly selected some of the long-range predictions from the CNN and added them to pixel grid-graph.
\begin{figure}[t]
\centering
        \includegraphics[width=\textwidth,trim=0.0in -0.in -0.0in -0.4in,clip]{figs/noisy_affs_comparison.pdf}
    \caption{CNN predictions on a slice of the CREMI neuron segmentation challenge with and without additional noise. (\textbf{a}) Raw data (\textbf{b}) Original CNN predictions $F(x)$, where blue pixels represent boundary evidence (\textbf{c}) Under-clustering biased version $\tilde{F}_{+}(x;\mathcal{K})$ of the predictions defined in Eq. \ref{eq:noise_biased_predictions} with $\mathcal{K}=8$ (\textbf{d}) Over-clustering biased version $\tilde{F}_{-}(x;\mathcal{K})$. Long-range predictions are not shown.
    }
    \label{fig:noisy_affs}
\end{figure}
\begin{table}
    \centering
    % \small
    \vspace*{0.6em}
        \begin{tabular}{l M{7em} M{7em}}
          \algname{} linkage & AP  & Bias $\beta$ \\ \midrule
          Average & 34.3 & 0.35 \\
          Average + CLC & 33.9 & 0.25\\
          Max + CLC & 32.5 & 0.50 \\
          Abs Max & 32.1 & 0.45\\
          Sum + CLC & 31.9 & 0.55 \\
          Sum & 31.3 & 0.55 \\
          Max & 24.3 & 0.85 \\
          Min & 0.00 & 0.50 \\
          Min + CLC & 0.00 & 0.50 \\
        \end{tabular}
    \vspace*{2em}
    \caption{Average Precision (AP) scores achieved by different versions of \algname{} and chosen bias parameters $\beta$ on the cityscapes validation set. A bias value $\beta=0$ returns one single cluster. CLC stands for cannot-link constraints.}
    \label{tab:extended_results_cityscapes_val}
\end{table}

@@

>>>>

\begin{algorithm*}
  \caption{Implementation of \algname{}, generalized algorithm for signed graph partitioning}
\hspace*{\algorithmicindent} \textbf{Input:} $\mathcal{G}(V,E,w^+,w^-)$ with $N$ nodes and $M$ edges; boolean \texttt{{\color{blue}addCannotLinkConstraints}} \\
\hspace*{\algorithmicindent} \textbf{Output:} Final clustering \\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]
      \State $\tilde{\mathcal{G}}(\tilde{V},\tilde{E}) \gets \mathcal{G}(V,E,w^+,w^-)$  \Comment{Init. contracted graph}
      \State \texttt{UF} $\gets$ initUnionFind($V$) \Comment{Init. data structure representing clustering}
        \State PQ.push$(|w_e|, e) \quad \forall e \in E $  \Comment{Init. priority queue in desc. order of $|w_e|=|w_e^+ - w_e^-|$, $\mathcal{O}(|E|)$}
        \State \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$ \Comment{Init. cannot-link constraints}
    \State
      \While{PQ is \textbf{not} empty}
        \State $\tilde{w}, e_{uv} \gets $ PQ.popHighest() \Comment{$\mathcal{O}(\log |E|)$}
        \State \textbf{assert} \texttt{UF}.find($u$) $\neq$ \texttt{UF}.find($v$) \Comment{Edges in PQ always link nodes in different clusters}
        \If{({\color{green}\textbf{$\tilde{w} > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
          \State PQ, \texttt{canBeMerged}, $\tilde{E}$ $\gets$ \textsc{UpdateNeighbors}($u,v$)
          \State $\tilde{V} \gets \tilde{V} \setminus \{ v\}$, $\quad \tilde{E} \gets \tilde{E} \setminus \{ e_{uv}\}$ \Comment{Update contracted graph}
          \State \texttt{UF}.merge($u,v$) \Comment{Merge clusters, $\mathcal{O}(\alpha(|E|))$}
        \ElsIf{({\color{red}\textbf{$\tilde{\cost} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLinkConstraints}}}
          \State \texttt{canBeMerged}$[e_{uv}] \gets$ \texttt{False} \Comment{Constrain the two clusters}
        \EndIf
      \EndWhile
      \State
      \Return Final clustering given by union-find data structure  \texttt{UF}
  \end{algorithmic}
  \hspace*{1.5cm} 
    \begin{algorithmic}[1]
    \Function{UpdateNeighbors}{$u,v$}
      \State $\mathcal{N}_u = \{ t \in \tilde{V} | e_{ut}\in \tilde{E}  \}$
      \State $\mathcal{N}_v = \{ t \in \tilde{V} | e_{vt}\in \tilde{E}  \}$ 
      \For{$t \in \mathcal{N}_v$ } \Comment{Loop over neighbors in $\tilde{\mathcal{G}}$ of deleted node $v$}
        \State $\tilde{E} \gets \tilde{E} \setminus \{e_{vt}\}$
        \State $\tilde{w}_{vt} \gets$ PQ.delete($e_{vt}$) \Comment{$\mathcal{O}(\log |E|)$}
        \State \texttt{canBeMerged}$[e_{ut}] \gets$ \texttt{canBeMerged}$[e_{ut}]$ \textbf{and} \texttt{canBeMerged}$[e_{vt}]$
        \If{$t \in \mathcal{N}_u$ }\Comment{$t$ is a common neighbor of $u$ and $v$}
          \State $\tilde{w}_{ut} \gets$ PQ.delete($e_{ut}$)  \Comment{$\mathcal{O}(\log |E|)$}
          \State PQ.push($ |f(\tilde{w}_{ut}, \tilde{w}_{vt})|, e_{ut}$) \Comment{$\mathcal{O}(\log |E|)$  }
        \Else
          \State $\tilde{E} \gets \tilde{E} \cup \{e_{ut}\}$
          \State PQ.push($ |\tilde{w}_{vt}|, e_{ut}$) \Comment{$\mathcal{O}(\log |E|)$}
        \EndIf
      \EndFor
      \State
      \Return PQ, \texttt{canBeMerged}, $\tilde{E}$
    \EndFunction
  \end{algorithmic}
  \label{detailed_alg}
\end{algorithm*}

@@

\begin{figure*}[t]
        \centering
        \includegraphics[width=0.7\textwidth]{./figs/proof_abs_max_example.pdf} % left bottom right top
\caption{\algname{} with \emph{AbsMax} linkage: Example representing the only case of edge contraction $e_{uv}$ that would introduce a positive attractive interaction between two constrained clusters. Note this can actually never happen with an \emph{AbsMax} linkage, because edge $e_{ut}$ has a lower absolute priority as compared to $e_{uv}$, so clusters $u$ and $t$ cannot have been constrained before $u$ and $v$ are merged.
}
\label{fig:abs_max_proof_example}  
\end{figure*}
\begin{algorithm*}[t]
  \caption{Mutex Watershed Algorithm proposed by \cite{wolf2018mutex}}
\hspace*{\algorithmicindent} \textbf{Input:} $\mathcal{G}(V,E,w^+,w^-)$ with $N$ nodes and $M$ edges \\
\hspace*{\algorithmicindent} \textbf{Output:} Final clustering \\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]
      \State \texttt{UF} $\gets$ initUnionFind($V$) 
      \For{$(u,v)=e\in E$ in descending order of $|w_e|=|w_e^+ - w_e^-|$}
        \If{\texttt{UF}.find($u$) $\neq$ \texttt{UF}.find($v$)} \Comment{Check if $u,v$ are already in the same cluster}
          \If{({\color{green}\textbf{$w_e > 0$}}) \textbf{and} \texttt{canBeMerged}($u,v$)}  \Comment{Check for cannot-link constraints}
            \State \texttt{UF}.merge($u,v$) and inherit constraints of parent clusters
          \ElsIf{({\color{red}\textbf{$w_e \leq 0$}})}
            \State Add cannot-link constraints between parent clusters of $u,v$
          \EndIf
        \EndIf
      \EndFor
      \State
      \Return Final clustering given by union-find data structure \texttt{UF}
  \end{algorithmic}
  \label{alg:mutex_watershed}
\end{algorithm*}

@@

In the field of image processing there are several ways of adding noise to an image, among which the most common are Gaussian noise or Poisson shot noise. 
In these cases, the noise of one pixel does not correlate with its neighboring noise values. On the other hand, predictions of a CNN are known to be spatially correlated. 
Thus, we used Perlin noise\footnote{In our experiments, we used an open-source implementation of simplex noise \cite{perlin2001noise}, which is an improved version of Perlin noise \cite{perlin1985image}}, one of the most common gradient noises used in procedural pattern generation. This type of noise $n(x)\in[0,1]$ generates spatial random patterns that are locally smooth but have large and diverse variations on bigger scales. We then combined it with the CNN predictions $p(x)$ in the two following ways: 
\begin{equation}\label{eq:noise_biased_predictions}
\tilde{F}_{\pm}(x;\mathcal{K})=F(x)\pm\big|\mathcal{K}\cdot\max\left(\pm N(x),0\right)\big|,
\end{equation}
where  $N(x)=\mathrm{Logit}[n(x)]$; $F(x)=\mathrm{Logit}[p(x)]$ and $\mathcal{K}\in \mathbb{R}^+$ is a positive factor representing the amount of added noise. $\tilde{F}_{+}(x;\mathcal{K})$ represents then a under-clustering biased prediction, such that the probability for two pixels to be in the same cluster is increased only if $N(x)>0$ (see Fig. \hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}b}), whereas $\tilde{F}_{-}(x;\mathcal{K})$ is a over-clustering biased prediction with decreased probabilities when $N(x)<0$ (Fig. \hyperref[fig:noisy_affs]{\ref*{fig:noisy_affs}c}).
In the implementation we used, the noise can be generated in an arbitrary number of dimensions and a smoothing factor can be specified for each direction independently. In our experiments, each pixel is represented by a node in the grid-graph and it is linked to $n_{\mathrm{nb}}$ other nodes by short- and long-range edges. Thus, the output of our CNN model has $n_{\mathrm{nb}}$ channels: for each pixel / voxel, it outputs $n_{\mathrm{nb}}$ values representing the weights of different edge connections. We then generated a 4-dimensional noise that matches the dimension of the CNN output. The data is highly anisotropic, i.e. it has a lower resolution in one of the dimensions. Due to this fact, we chose different smoothing parameters to generate the noise in different directions. \TODO{Give these smoothing parameters...}

The experiments summarized in Fig. \ref{fig:noise_plots} were performed in the following way: for each value $\mathcal{K}$, 30 random noise samples were drawn, from which median and percentiles statistics were computed for each different linkage criteria. For each sample, we randomly selected some of the long-range predictions from the CNN and added them to pixel grid-graph.
\begin{figure*}[t]
\centering
        \includegraphics[width=\textwidth,trim=0.0in -0.in -0.0in -0.4in,clip]{figs/noisy_affs_comparison.pdf}
    \caption{CNN predictions on a slice of the CREMI neuron segmentation challenge with and without additional noise. (\textbf{a}) Raw data (\textbf{b}) Original CNN predictions $F(x)$, where blue pixels represent boundary evidence (\textbf{c}) Under-clustering biased version $\tilde{F}_{+}(x;\mathcal{K})$ of the predictions defined in Eq. \ref{eq:noise_biased_predictions} with $\mathcal{K}=8$ (\textbf{d}) Over-clustering biased version $\tilde{F}_{-}(x;\mathcal{K})$. Long-range predictions are not shown.
    }
    \label{fig:noisy_affs}
\end{figure*}
\begin{table}
    \centering
    % \small
    \vspace*{0.6em}
        \begin{tabular}{l M{7em} M{7em}}
          \algname{} linkage & AP  & Bias $\beta$ \\ \midrule
          Average & 34.3 & 0.35 \\
          Average + CLC & 33.9 & 0.25\\
          Max + CLC & 32.5 & 0.50 \\
          Abs Max & 32.1 & 0.45\\
          Sum + CLC & 31.9 & 0.55 \\
          Sum & 31.3 & 0.55 \\
          Max & 24.3 & 0.85 \\
          Min & 0.00 & 0.50 \\
          Min + CLC & 0.00 & 0.50 \\
        \end{tabular}
    \vspace*{2em}
    \caption{Average Precision (AP) scores achieved by different versions of \algname{} and chosen bias parameters $\beta$ on the cityscapes validation set. A bias value $\beta=0$ returns one single cluster. CLC stands for cannot-link constraints.}
    \label{tab:extended_results_cityscapes_val}
\end{table}

@@

\subsection{Ultrametrics} 
Thus, to prove that $(V, d_{T})$ is an ultrametric, we only need to prove that
\begin{equation}
\interact{}_{T}(u,v) \geq \min \{\interact{}_{T}(u,t), \interact{}_{T}(v,t)\}
\end{equation}
 for every distinct $u,v,t\in V$. In other words, given two leaves nodes $u,v\in V$, the depth $\interact{}_{T}(u,v)$ associated to their least common ancestor $i\in T$ should be both lower than the depth of any $i$-descendant node in $T$ and higher than any $i$-ancestor node in $T$:
 % that have the most positive interaction   two clusters merged by the algorithm will always have an interaction that is more negative as compared to all clusters already merged and more positive than all clusters that will be merged at later iterations of the algorithm.
\begin{equation}
\interact{}_{T}(u,v) \geq \interact{}_{T}(u,t) \Leftrightarrow T[u \vee t] \subseteq T[u \vee v] 
\end{equation}
 This happens only if, at every iteration, Algorithm \ref{main_alg} merges pairs of clusters with lower and lower interactions, which is true for only certain choices of linkage criteria. %In the next section \ref{sec:alg_update_rules}, we will show that this happens only for certain linkages and only when constraints are not enforced
